We do some simple analysis experiments with the fantom 5 data.

First, let's load the expression set
```{r}
source("./eset_analysis_tools.R")
load("data/f5_expressionset.Rdata")
```

We are interested in generating cell-specific signatures. 
Single cell experiments are annotated with sample_type 'primary cell'. 
```{r}
pdata = pData(expr.set)
eset.primary = expr.set[,pdata$sample_type == "primary cell"]
```

Merge technichal replicates to single sample. 
```{r}
tech_reps = unique(pData(eset.primary)[pData(eset.primary)$tech_rep == TRUE,]["obo_id"])
print(tech_reps)
eset.primary.notechrep = eset.primary[,]
for (tech_rep in tech_reps[,1]) { 
  sample.ids = which(pData(eset.primary.notechrep)$obo_id == tech_rep)
  new.name = pData(eset.primary.notechrep)[sample.ids[1],]$name
  eset.primary.notechrep = mergeSamples(eset.primary.notechrep, sample.ids, new.name)
}
dim(eset.primary.notechrep)
dim(eset.primary)

save(eset.primary.notechrep, file="data/f5_eset_primary_cells.Rdata")
```


Correlation Matrix with hierarchical clustering:
```{r}
corr.mat = cor(exprs(expr.set))
heatmap(corr.mat)
```

Principal component Analysis.
Since this is fairly slow, we need to do some preprocessing. We can remove samples with high correlation and low variance.
```{r}

```