We do some simple analysis experiments with the fantom 5 data.

First, let's load the expression set
```{r}
source("./eset_analysis_tools.R")
load("data/f5_expressionset.Rdata")
```

We are interested in generating cell-specific signatures. 
Single cell experiments are annotated with sample_type 'primary cell'. 
```{r}
pdata = pData(expr.set)
eset.primary = expr.set[,pdata$sample_type == "primary cell"]
```

## Merge technichal replicates to single sample. 
```{r}
tech_reps = unique(pData(eset.primary)[pData(eset.primary)$tech_rep == TRUE,]["obo_id"])
print(tech_reps)
eset.primary.notechrep = eset.primary[,]
for (tech_rep in tech_reps[,1]) { 
  sample.ids = which(pData(eset.primary.notechrep)$obo_id == tech_rep)
  new.name = pData(eset.primary.notechrep)[sample.ids[1],]$name
  eset.primary.notechrep = mergeSamples(eset.primary.notechrep, sample.ids, new.name)
}
dim(eset.primary.notechrep)
dim(eset.primary)

save(eset.primary.notechrep, file="data/f5_eset_primary_cells.Rdata")
```


## Correlation Matrix with hierarchical clustering:
Maybe use https://www.r-bloggers.com/large-correlation-in-parallel/? 
Alternative hiearchical clustering: http://research.stowers-institute.org/efg/R/Visualization/cor-cluster/
```{r}
getName = function(lib_id) {
  return(paste(pData(expr.set)[lib_id, 'obo_id'], "-", pData(expr.set)[lib_id, 'name']))
}
```
```{r}
load("R_tmp/corr.mat.Rdata")
write.table(corr.mat, file="data/corr_mat.primary.tsv")
rownames(corr.mat) = getName(rownames(corr.mat))
colnames(corr.mat) = getName(colnames(corr.mat))
dissim = 1-corr.mat
dist = as.dist(corr.mat)
clust = hclust(dist)
par(cex=0.2, mar=c(30, 4, 4, 2)+0.1)
plot(as.dendrogram(clust))
```


## Annotate the dendrogram
http://stackoverflow.com/questions/33450549/r-python-heirarchical-clustering-dendrogram-annotation

## Principal component Analysis.
Since this is fairly slow, we need to do some preprocessing. We can remove samples with high correlation and low variance.
```{r}

```